Reduced plasticity and relative variance in physiological rates of ectotherm populations under climate change

### 2024-06-23 ms.qmd
UPdating pub bias. Realise I was missing information about the actual model results

Funnel plots did not show any noticeable deviation from the typical funnel shape for any of the effect size estimates (@fig-s2).

@@

@@

@@

@@

>>>>

@@

  post_pb_lnrr <- posterior_samples(model_full_lnrr_pb, "^b_V")[,1]

@@

  post_pb_lncvr <- posterior_samples(model_full_lncvr_pb, "^b_V")[,1]

@@

  model_full_lnvr_pb <- posterior_samples(model_full_lnvr_pb, "^b_V")[,1]

@@

Funnel plots did not show any noticeable deviation from the typical funnel shape for any of the effect size estimates (@fig-s2). Meta-regression models including sampling variance as a moderator also suggested no relationship with effect size for $lnRR_{Q_{10}}$ ($\beta$ = `r mean(post_pb_lnrr)`, 95% CI: `r quantile(post_pb_lnrr, 0.025)` to `r quantile(post_pb_lnrr, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(post_pb_lnrr))`), $lnCVR_{Q_{10}}$ ($\beta$ = `r mean(post_pb_lncvr)`, 95% CI: `r quantile(post_pb_lncvr, 0.025)` to `r quantile(post_pb_lncvr, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(post_pb_lncvr))`) or $lnVR_{Q_{10}}$ ($\beta$ = `r mean(model_full_lnvr_pb)`, 95% CI: `r quantile(model_full_lnvr_pb, 0.025)` to `r quantile(model_full_lnvr_pb, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(model_full_lnvr_pb))`).
